### 2015-01-31 docs/report/serialization_transference.tex
Fixed numbers, created macros for benchmarks

\section*{Serialization and Transference}

@@

>>>>

\section{Serialization and Transference}

@@

\subsection{Benchmarks}
To verify the above we put together two benchmarks that aim to verify the difference between invoking \textit{postMessage} with and without structured cloning for a \textit{TypedArray}. Both transfer a \textit{TypedArray} back and forth between the UI thread and a worker; the only difference between the two is that one has 100000 elements in the \textit{TypedArray} and the other one 1000000.

\subsubsection{With 100000 elements}
The following is the code for the benchmark:
\bmcode{http://js-perf}{js_lang.tex}

These were the results:
\bmcode{Results with 100000 elements}{js_lang.tex}

\subsubsection{With 1000000 elements}
The following is the code for the benchmark:
\bmcode{http://js-perf}{js_lang.tex}

These were the results:
\bmcode{Results with 1000000 elements}{js_lang.tex}

\subsubsection{Conclusion}
As we can see from the previous results increasing the amount of elements by 10x does not change the amount of operations that can be performed when using \textit{Transferable} objects, it scales. On the other hand, the amount of operations that can be performed with structure cloning greatly decreases.

For that reason we will only work with \textit{Typed Arrays} and all of them will be passed to/from Web Workers by transferring their ownership.
